---
title: "Post-Release Contact Rates of Razorback Sucker"
author: "B. Kesner And C. Ehlo"
format: html
echo: false
editor: source
---

```{r}
#| warning: false


MinReleaseYear = 2015 # Limit to fish release on or after this year

source("ReachLogisticPostRelease.R")
```

## Methodology

A post-release contact analysis was developed based on PIT scanning for release fiscal year (FY; October through September), season and MSCP reach of release. The relationship of TL (mm) at release and contact probability was modeled using zero inflated logistic regression. All release (stocking) records for razorback suckers with a TL at release were utilized for this analysis. Estimated detection probabilities are a combination of survival and detectability, because we cannot assume the entire razorback sucker population is detected via PIT scanning. These probabilities are assumed to be an index of apparent survival. The analysis was restricted to fish released on or after FY `r MinReleaseYear`.

Seasons were based on patterns of stocking and spawning behavior and not traditional seasons. Early spring was February through March (peak spawning season), Late spring was April through May (post-spawning), summer-fall was June through October (hot months with few stockings), and winter (November through January). These seasons can be adjusted in the ReachLogisticPostRelease.R script. Summer-fall was removed from the model due to a lack of consistent release records across years and reaches.

The glmTMB package in R was used to assess the parameters of the zero-inflated logistic regression model. Release TL and reach were fully modeled (additive and interactive effects) whereas release FY was treated as an additive factor only (Contacted ~ ReleaseTL * Season * ReleaseReach + ReleaseFY). For each MSCP Reach with significant razorback sucker stockings (Reaches 2 through 4), the resultant model was used to predict values of detectability among release reach, release FY, season, and size at release (Reach 2 @fig-DALReach2, Reach 3 @fig-DALReach3, and Reach 4 @fig-DALReach4.). Release records were grouped by release reach, release FY, season, and TL bin \[10 mm\] to form release cohorts and contact data was used to calculated actual detection proportions for each cohort. These proportions were plotted (point data) for comparison with model results. 

 Size histograms for each season and reach were also plotted for fish contacted and not contacted. If post-stocking survival is dependent on size at release for a given season and reach of release, then the size frequency histogram for post-release contacted fish should be shifted (different mean, median, and mode) compared to non-contacted fish (Reach 2 @fig-Hist2, Reach 3 @fig-Hist3, and Reach 4 @fig-Hist4).


```{r}
#| label: fig-DALReach2
#| fig-cap: "Post-release contact probability Reach 2."
#| warning: false
DALGraphR2

```

```{r}
#| label: fig-DALReach3
#| fig-cap: "Post-release contact probability Reach 3."
#| warning: false
DALGraphR3

```

```{r}
#| label: fig-DALReach4
#| fig-cap: "Post-release contact probability Reach 4."
#| warning: false
DALGraphR4

```

The size distribution of razorback sucker contacted (blue) or not contacted (grey) post-release among different seasons shown for Reach 2 @fig-Hist2, Reach 3 @fig-Hist3, and Reach 4 @fig-Hist4.

```{r}
#| label: fig-Hist2
#| fig-cap: "Release size (TL in mm) of razorback sucker contacted (blue) and not contacted (grey) post-release in Reach 2."
#| warning: false
HistReach2

```

```{r}
#| label: fig-Hist3
#| fig-cap: "Release size (TL in mm) of razorback sucker contacted (blue) and not contacted (grey) post-release in Reach 3."
#| warning: false
HistReach3

```

```{r}
#| label: fig-Hist4
#| fig-cap: "Release size (TL in mm) of razorback sucker contacted (blue) and not contacted (grey) post-release in Reach 4."
#| warning: false
HistReach4

```